Storing messages with multipartite neural cliques

### 2014-07-07 Articles/article.tex
...

@@

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum}
		\label{asumsum}
		\begin{algorithmic}
		\Require{}
		\Statex
		\While{step < I}
		\If {$i\geq maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	Ambiguities would occur in a perfect associative memory if at least two messages would be identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.

@@

		New rule : Improves the retrieval rate for multiple iterations and/or corrupted messages.

		The simulations agree with the analytical results for density and error rate.

@@

	To be really precise : (ne pas oublier de tenir compte changement des lois)
	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
	\end{align*}

@@

	\section{Resilience}
	Spéculations en Français :

	Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)

	Marche mieux pour des bruits importants

@@

	\newpage
	$\,$
	\newpage
	\begin{figure}
		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}

@@

>>>>

\newcommand*\Let[2]{\State #1 $\gets$ #2}
\algrenewcommand\algorithmicrequire{\textbf{Precondition:}}
\algrenewcommand\algorithmicensure{\textbf{Postcondition:}}

@@

		$w = a$	is optimal
		\begin{algorithm}
		\caption{$a$-sum of sum}
		\label{asumsum}
		\begin{algorithmic}
		\Require{}
		\Statex
		\While{step < I}
		\Let{a}{b}
		\If {$i\ge maxval$}
   	 	\State $i\gets 0$
		\Else
    		\If {$i+k\leq maxval$}
        	\State $i\gets i+k$ \Comment{$\oplus$: bitwise exclusive-or}
    		\EndIf
		\EndIf
		\EndWhile
		\end{algorithmic}
		\end{algorithm}

@@

	Ambiguities would occur in a perfect associative memory if at least two messages were identical over non-erased letters. The probability it doesn't happen is $ (1-{l \choose a}^{c - c_e})^{m-1}$.

@@

		The variant rule improves the retrieval rate for multiple iterations and/or corrupted messages.

		The simulations agree with the analytical results for both density and error rate.

@@

	To be really precise : (ne pas oublier de tenir compte changement des lois, formule inexacte pour l'instant)
	\begin{align*}
	&P_{retrieve} = \left [ \sum_{n = 1}^{a(c-1) + \gamma} \left [ \sum_{k = 1}^{a} { a \choose k }   P(n_{gc} = n)^k P(n_{gc} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a} \right ]^{c - c_e}\\ 
	 &\times \left [ \sum_{y = 0}^a \left( \frac{{l-y \choose a} - \sum_{z = y+1}^{a} {l-z \choose a }}{{l \choose a}}\right)\sum_{n = 1}^{a(c-1) +\gamma} \left[ \sum_{k = 1}^a { a \choose k } P(n_{ge} = n)^k P(n_{ge} > n)^{a-k} \right ] P(n_{bc} < n)^{l-a - y} P(n_{abc} < n)^{a - y} \right ]^{c_e}
	\end{align*}

@@

	\section{Resilience}
	%Spéculations en Français 
	%Peut-être un intérêt pour cluter based associative memories build from unreliable storage : si une arête porte moins d'info, on peut peut-être en supprimer plus (mais rajout ?!)

	As information is shared accross connections with multiple activated neurons per cluster, they are more resilient to network damages.

	%Marche mieux pour des bruits importants

@@

	\newpage
	%$\,$
	%\newpage
	\begin{figure}
		\includegraphics[scale=0.55]{Courbes/5portant_psi_c8l256e4}
		\caption{Comparison between different number of activities per cluster :  8 clusters, 256 neurons per cluster, 1000 sampled messages, pools of 5 networks}
	\end{figure}

@@

	$\eta_{m, \psi} = P_{retrieve} m  \frac{2 \left(c \log_2{l \choose a } - \log_2(m) + 1 \right)}{c(c-1)l^2} \times (1-{l \choose a}^{c - c_e})^{-(m-1)} \times \frac{1}{1 + \psi \log_2(\psi) +(1-\psi) \log_2(1-\psi)} $

	$\eta_\psi = max_x \eta_{x, \psi}$
